---
title: "Predicting Iris species"
author: "Andrés Sierra-Ricaurte"
date: "13/9/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The database
I wanted to make and app where the user can select the values for some flower measurements and the app returns a predicted species.

For this task I fit two models with the Iris dataset available in R. Here the first values:

```{r, echo=FALSE, comment=""}
head(iris)
```

## The Plots
I provided to the user a visualization of the data, because it is important to have in mind how is the data distributed. I also add a purple point for the values selected by the user in the sidebar panel.
```{r}
library(ggplot2)
p <- ggplot(data=iris, aes(x=Petal.Width, y=Petal.Length, color=Species))
p + geom_point() + geom_point(aes(x=1, y=3), color="purple", size=3) + theme_bw()
```

## Random Forest
Using the `caret` package and creating data partition (p=0.7) for training and testing datasets, I fitted a random forest model and predict the species for the measures selected by the user.
I also provided the accuracy of the model when predicting the testing dataset:

```{r, comment="", warning=FALSE, message=FALSE}
library(caret)
my_data <- iris[,3:5]
inTrain <- createDataPartition(y=my_data$Species, p=0.7, list=F)
    training <- my_data[inTrain, ]
    testing <- my_data[-inTrain, ]
    model1 <- train(Species~., data=training, method="rf")
    a <- confusionMatrix(testing$Species, predict(model1, testing[,-3]))
    a$overall
```

## Linear discriminant analysis
Using the `caret` package and creating data partition (p=0.7) for training and testing datasets, I fitted a linear discriminant analysis (lda) model and predict the species for the measures selected by the user.
I also provided the accuracy of the model when predicting the testing dataset:

```{r, comment="", warning=FALSE, message=FALSE}
library(caret)
my_data <- iris[,3:5]
inTrain <- createDataPartition(y=my_data$Species, p=0.7, list=F)
    training <- my_data[inTrain, ]
    testing <- my_data[-inTrain, ]
    model2 <- train(Species~., data=training, method="lda")
    a <- confusionMatrix(testing$Species, predict(model2, testing[,-3]))
    a$overall
```